\documentclass{article}
\usepackage[top=0.2cm, left=1cm, right=1cm, bottom=0.2cm]{geometry}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{enumitem}

\setlist{nosep}


\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\title{Vlad Komodey. Backend Developer \vspace{-3em}}
\author{}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}
\section*{Sources\vspace{-0.5em}}
\begin{itemize}
    \item \href{https://github.com/vkomodey}{Github}
    \item \href{https://www.linkedin.com/in/vladislav-komodey-2b1b4aa0/}{Linkedin}
\end{itemize}

\vspace{-1em}
\section*{Location\vspace{-0.5em}} Frisco, TX. USA

\section*{Professional Summary}

A hardworking and passionate person with strong organizational skills eager. I
love to work with complex projects and design systems. Keen on studying new
technologies. Interested in good architecture designs (e.g. LMax). Prefer simplicity over complexity.
Ready to help the team achieve company goals.

\vspace{-1.5em}
\section*{Skills}

\begin{multicols}{2}
\begin{enumerate}
    \item Divide and conquer. Split complex into easy
    \item Ability to write bug-free and well-tested code
    \item Avoid premature optimization
    \item Designing systems from scratch
    \item Backend performance optimization
    \item Project planning
    \item Controlling healthy project lifecycle
    \item Mentoring people
    \item Diving into business need before implementing

\end{enumerate}
\end{multicols}

\vspace{-2em}
\section*{Technologies}
\begin{multicols}{2}
    \begin{enumerate}
        \item Frameworks Node.js: Express, Nest
        \item Frameworks Python: Fast API, Flask
        \item Tests: Jest, Mocha
        \item Cloud: AWS + a little bit GCP
        \item DBs: MongoDB, PostgreSQL, Redis
        \item CI/CD: Jetbrains Teamcity
        \item Application Lifecycle: Docker, Kubernetes
        \item Linux enjoyer
        \item Web3: Ethereum, Polygon
        \item Frontend(React.js) - but when it is really required
    \end{enumerate}
\end{multicols}


\section*{Work history}

\textbf{Human Protocol}. Backend Developer/Engineering Manager.\hspace*{0pt}\hfill March/2021 | September/2022

\begin{itemize}
 \item Designed and implemented semi-decentralized protocolfor annotating datasets for machine learning purposes
 \item Initialized cloud infrastructure in AWS
 \item Leading the team of backend and frontend developers
 \item Improved security protection for the main application
 \item Developed smart contracts using Solidity
 \item Hiring developers
 \item Mentoring junior and middle developers
\end{itemize}

\par\noindent\rule{\textwidth}{0.4pt}
\textbf{Paralect}. Backend Lead Developer.\hspace*{0pt}\hfill October/2015 | February/2021
\begin{itemize}
    \item Designed and implemented fraud and payment monitoring services from scratch
    \item Performance optimization of core transaction process in the European bank
    \item Implemented and integrated performance testing into CI/CD process
    \item Designed the process to control tech debt for multiple dev squads
    \item Responsible for the full feature cycle (requirement elicitation, implementing, setting up the infra, shipping, demo)
\end{itemize}
\par\noindent\rule{\textwidth}{0.4pt}
\textbf{Avtodom}. Backend Developer.\hspace*{0pt}\hfill January 2017 | January 2023
\begin{itemize}
    \item Designed and developed ETL system for analyzing vehicle price
    \item Developed and incorporated ML model into the system above
    \item CI/CD process
\end{itemize}
\par\noindent\rule{\textwidth}{0.4pt}
\textbf{Exadel}. Backend Developer.\hspace*{0pt}\hfill December 2014 | October 2015

\begin{itemize}
\item Analytics system for the project related to the songs market
\end{itemize}

\vspace{-1.5em}
\section*{Education}
\textbf{Belarusian State University}\hspace*{0pt}\hfill September 2012 | June 2017 \\
Master's Degree. Faculty Of Applied Mathematics And Informatics
\end{document}
